EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
todo mocking
zero cov

% Look at benchmarks that always failed
\EVOSUITE failed to produce any test suite for benchmarks JXPATH-7 and
OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
BCEL-9 (highlighted in Table~\ref{table:results}).\TODO{look into details}

@@

>>>>

% Look at benchmarks that always failed
\EVOSUITE failed to produce any test suite for benchmarks JXPATH-7 and
OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
BCEL-9 (highlighted in Table~\ref{table:results}). All executions of
\EVOSUITE for JXPATH-7 failed in the instrumentation phase as a result
of exceeding Java's 64k limit on the size of methods. A trivial fix
would be to stop instrumenting before the limit is reached, at the
price of limited search guidance; a more effective solution would
involve identifying parts of the code that are worth instrumenting. A
missing dependency for OKHTTP-8 caused all executions---\emph{for all
  tools}---to fail. For the other mentioned benchmarks, the failure
reasons (in some cases related to sandboxing, mocking and timeouts)
will require further investigation.

% LA4J-3, LA4J-7: Phase INITIALIZATION lasted too long, Phase SEARCH lasted too long, 9 seconds more than allowed.

@@

% Mocking
\TODO{Add some stats on mocking}
